---
title       : mpgCalc
subtitle    : 
author      : Josh Gardner
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Fuel efficiency matters

1. Fuel is expensive!
2. Fuel-efficient vehicles reduce our carbon footprint

## So -- you want to know your car's mpg!

mpcCalc can help!

* Input basic information about your car
* Get an instant, reliable estimate of your overall mpg


--- .class #id 

## This app isn't just for car owners!

* Can be used for prospective car buyers--to evaluate claims made by car manufacturers, or to search for the ideal specifications needed to produce a desirable fuel economy.
* Car renters might also want a quick way to verify their vehicle's fuel economy to save on gas while traveling.

## How to use mpgCalc

**This is a turnkey system.** It's ready to use, with no setup required. 

* Input your vehicle's specifications (these items were specifically selected as both important to mpg estimation and as features every car owner would know)
* See the instant mpg calculation! The numbers and the visualization both update immediately with virtually no lag time.
* Compare your vehicle to the other cars in the dataset using the plot.

--- .class #id 

## Modeling Details

mpgCalc uses a linear regression model, built on the mtcars dataset, to generate estimates of mpg for the user-provided specifications.

*The model uses variables selected both for being strong predictors of mpg, but also as features every car owner would know.
* See the instant mpg calculation! 
* Input your vehicle's specifications (these items were specifically selected as both important to mpg estimation and The numbers and the visualization both update immediately with virtually no lag time.
* Compare your vehicle to the other cars in the dataset using the plot.


--- .class #id 
## Model Summary
```{r, echo=TRUE}
mtcars$am <- factor(mtcars$am)
appcarfit <- lm(mpg ~ cyl + hp + wt + am + gear, data = mtcars)
```

```{r, echo=TRUE}
summary(appcarfit)$coefficients
summary(appcarfit)$r.squared
```




